Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-12-02 paper/introduction.tex
add VR reference

Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
a portable Docker container, which conveniently exposes an HTTP API using the
Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
geometry was deliberately left adjustable, so that dependency of TBR on various
parameters may be explored. Nuclear data for simulation was extracted from the following sources, in order of preference: Fendl 3.1d \cite{fendl31d}; Jeff 3.3 \cite{jeff33}; and ENDF 7.1 \cite{2011ii}.

@@

\footnotetext[1]{A bug in the Muir distribution involving erronous normal sampling was recently uncovered (see https://github.com/openmc-dev/openmc/pull/1670), but is disregarded in the present approach-focused work.}

>>>>

Paramak facilitates simulation via OpenMC neutronics workflow that is enclosed in
a portable Docker container, which conveniently exposes an HTTP API using the
Python~3 \texttt{flask} package. For the purposes of our work, we used this setup to
simulate a point source with a Muir energy distribution \cite{openmcmuir}\footnotemark[1]
around~\SI{14.06}{\mega\electronvolt} to approximate a Deuterium-Tritium (D-T)
plasma neutron source. Illustrated in~\Fref{fig:model_diagram}, the simulated
geometry was deliberately left adjustable, so that dependency of TBR on various
parameters may be explored. Nuclear data for simulation was extracted from the following sources, in order of preference: Fendl 3.1d \cite{fendl31d}; Jeff 3.3 \cite{jeff33}; and ENDF 7.1 \cite{2011ii}.
To maintain model-agnostic approach, variance reduction (VR) techniques
were not used to accelerate the MC neutronics simulation~\cite{Kleijnen2013}.
It should be noted that depending on application, VR may constitute a viable
alternative to the presented work.

@@

\footnotetext[1]{A bug in the Muir distribution involving erronous normal
sampling was recently uncovered (see
\url{https://github.com/openmc-dev/openmc/pull/1670}), but is disregarded in the present approach-focused work.}
